---
title: "autoMrP"
author: "Broniecki, Philipp and Lucas Lemann and Reto Wüest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autoMrP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autoMrP)
```

In the past twenty years we have witnessed a surge in methodological innovations for small-area estimation. In short, scholars often have nationally representative survey data and would like to create sub-national, e.g., state-level, estimates based on these data. Multilevel regression with post-stratification (MrP) has emerged as the gold standard to achieve this goal \citep{selb2011estimating}. Different improvements to the original MrP model have been proposed and the latest developments combine insights from statistical learning and MrP to provide better estimates. This article introduces the \proglang{R} package \pkg{autoMrP} which allows users to fit traditional MrP models as well as leverage a number of prediction algorithms. This allows building optimized models for generating sub-national estimates from national survey data that outperform those generated by simple MrP models.

